---
title: "Metadata Walkthrough"
author: "Chris Jones"
date: "2024-03-13"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geometa)
library(terra)
library(sf)
```

## Load in our geospatial data and get crs and other information from it.

```{r data loading}
file_path <- "C://Users/chris/Projects/Metadata-Workshop/"
soy_data <- sf::read_sf(paste0(file_path, "data/USDA_APU_1_2016_SOYBEANS_ptfinal_utm/USDA_APU_1_2016_SOYBEANS_ptfinal_utm.shp"))
soy_crs <- sf::st_crs(soy_data)
soy_bounding_box <- sf::st_bbox(soy_data)

soy_data_proj <- sf::st_transform(soy_data, crs = st_crs("epsg:4326"))
soy_bounding_box <- sf::st_bbox(soy_data_proj)
```


## Metadata Info
Mandatory items are not commented out. 

```{r metadata}
md = ISOMetadata$new()
# md$setFileIdentifier("my-metadata-identifier")# use if there is this data is part of a nested set of data
# md$setParentIdentifier("my-parent-metadata-identifier") # use if there is this data is part of a nested set of data
md$setCharacterSet("utf8")
md$setLanguage("eng; USA")
md$setDateStamp(ISOdate(2024, 03, 13))
md$setMetadataStandardName("ISO 19115")
md$setMetadataStandardVersion("ISO 19115-1:2014")
# md$setDataSetURI("my-dataset-identifier")

```

## Identification info
Mandatory and expected items are not commented out while other items are commented out.

```{r pressure}
# Main identification information
ident <- ISODataIdentification$new()
ident$setAbstract("Soybean data collected for APU Field 1 and processing steps are provided in https://acsess.onlinelibrary.wiley.com/doi/10.1002/agg2.20474")
ident$setPurpose("This data was produced to create gridded maps of crop yield.")
ident$addCredit("Wayne P. Dulaney")
ident$addCredit("Martha C. Anderson")
ident$addCredit("Feng Gao")
ident$addCredit("Alan Stern")
ident$addCredit("Alex White")
ident$addStatus("completed")
ident$addLanguage("eng")
ident$addCharacterSet("utf8")
ident$addTopicCategory("farming")
ident$addTopicCategory("environment")

# Add responsible Party Contact information
rp <- ISOResponsibleParty$new()
rp$setIndividualName("Alex White")
rp$setOrganisationName("United States Department of Agriculture - Agricultural Research Service")
rp$setPositionName("Data Curator")
rp$setRole("pointOfContact")
contact <- ISOContact$new()
phone <- ISOTelephone$new()
phone$setVoice("myphonenumber")
# phone$setFacsimile("myfacsimile") # mandatory if voice not provided
contact$setPhone(phone)
address <- ISOAddress$new()
address$setDeliveryPoint("")
address$setCity("Beltsville")
address$setPostalCode("20705")
address$setCountry("USA")
address$setEmail("poc@usda.gov")
contact$setAddress(address)
## Add comment for DOI
# res <- ISOOnlineResource$new()
# res$setLinkage("http://somelink")
# res$setName("someresourcename")
# contact$setOnlineResource(res)
rp$setContactInfo(contact)
md$addContact(rp)

# Add in Citation information for resource
ct <- ISOCitation$new()
ct$setTitle("Gridded Yield Data")
d <- ISODate$new()
d$setDate(ISOdate(2024, 02, 18))
d$setDateType("publication")
ct$addDate(d)
# ct$setEdition("1.0")
# ct$setEditionDate(as.Date(ISOdate(2024, 02, 18)))
ct$addIdentifier(ISOMetaIdentifier$new(code = "identifier"))
ct$addPresentationForm("mapDigital")
ct$addCitedResponsibleParty(rp)
ident$setCitation(ct)

# Add Keywords for identifying resource
kwds <- ISOKeywords$new()
kwds$addKeyword("agriculture")
kwds$addKeyword("USDA-ARS")
kwds$addKeyword("Gridded yield data")
kwds$setKeywordType("theme")
th <- ISOCitation$new()
th$setTitle("General")
th$addDate(d)
kwds$setThesaurusName(th)
ident$addKeywords(kwds)

# graphic overview (only if applicable)
# go1 <- ISOBrowseGraphic$new(
#   fileName = "http://wwww.somefile.org/png1",
#   fileDescription = "Map Overview 1",
#   fileType = "image/png"
# )
# go2 <- ISOBrowseGraphic$new(
#   fileName = "http://www.somefile.org/png2",
#   fileDescription = "Map Overview 2",
#   fileType = "image/png"
# )
# ident$addGraphicOverview(go1)
# ident$addGraphicOverview(go2)

# Spatial Reference System
rs <- ISOReferenceSystem$new()
rsId <- ISOReferenceIdentifier$new(code = paste0(soy_crs$epsg), codeSpace = "EPSG")
rs$setReferenceSystemIdentifier(rsId)
md$addReferenceSystemInfo(rs)

#maintenance information
# mi <- ISOMaintenanceInformation$new()
# mi$setMaintenanceFrequency("daily")
# ident$addResourceMaintenance(mi)

#adding extent
extent <- ISOExtent$new()
bbox <- 
  ISOGeographicBoundingBox$new(minx = soy_bounding_box$xmin, 
                               miny = soy_bounding_box$ymin, 
                               maxx = soy_bounding_box$xmax, 
                               maxy = soy_bounding_box$ymax)
extent$addGeographicElement(bbox)
ident$addExtent(extent)

#supplementalInformation
# ident$setSupplementalInformation("some additional information")

#spatial representation type
ident$addSpatialRepresentationType("vector")

```

## Constraint Information

```{r constraints}
# #adding access legal constraints
# #for INSPIRE controlled terms on access legal constraints, please browse the INSPIRE registry:
# # http://inspire.ec.europa.eu/metadata-codelist/LimitationsOnPublicAccess/
# lc <- ISOLegalConstraints$new()
# lc$addAccessConstraint("otherRestrictions")
# lc$addOtherConstraint(ISOAnchor$new(
#   href = "http://inspire.ec.europa.eu/metadata-codelist/LimitationsOnPublicAccess/INSPIRE_Directive_Article13_1a",
#   name = "public access limited according to Article 13(1)(a) of the INSPIRE Directive"
# ))
# ident$addResourceConstraints(lc)
# 
# #adding use legal constraints
# #for INSPIRE controlled terms on use legal constraints, please browse the INSPIRE registry:
# # http://inspire.ec.europa.eu/metadata-codelist/ConditionsApplyingToAccessAndUse
# lc2 <- ISOLegalConstraints$new()
# lc2$addUseLimitation("limitation1")
# lc2$addUseLimitation("limitation2")
# lc2$addUseLimitation("limitation3")
# lc2$addAccessConstraint("otherRestrictions")
# lc2$addOtherConstraint(ISOAnchor$new(
#   href = "http://inspire.ec.europa.eu/metadata-codelist/ConditionsApplyingToAccessAndUse/noConditionsApply",
#   name = "No conditions apply to access and use."
# ))
# ident$addResourceConstraints(lc2)
# 
# #adding security constraints
# sc <- ISOSecurityConstraints$new()
# sc$setClassification("secret")
# sc$setUserNote("ultra secret")
# sc$setClassificationSystem("no classification in particular")
# sc$setHandlingDescription("description")
# ident$addResourceConstraints(sc)

```


## Spatial Representation Info
Mandatory and expected items are not commented out while other items are commented out.
Spatial Representation type codes:
vector - vector data is used to represent geographic data
grid - grid data is used to represent geographic data
textTable - textual or tabular data is used to represent geographic data
tin - triangulated irregular network
stereoModel - three-dimensional view formed by the intersecting homologous rays of an overlapping pair of images
video - scene from a video recording

```{r pressure}
# Vector Spatial Representation
vsr <- ISOVectorSpatialRepresentation$new()
vsr$setTopologyLevel("geometryOnly")
geomObject <- ISOGeometricObjects$new()
geomObject$setGeometricObjectType("point")
geomObject$setGeometricObjectCount(nrow(soy_data))
vsr$addGeometricObjects(geomObject)
md$addSpatialRepresentationInfo(vsr)
md$addIdentificationInfo(ident)
```

## Distribution Info 
Mandatory and expected items are not commented out while other items are commented out.

```{r pressure}
# distrib <- ISODistribution$new()
# dto <- ISODigitalTransferOptions$new()
# for(i in 1:3){
#   or <- ISOOnlineResource$new()
#   or$setLinkage(paste0("http://somelink",i))
#   or$setName(paste0("name",i))
#   or$setDescription(paste0("description",i))
#   or$setProtocol("WWW:LINK-1.0-http--link")
#   dto$addOnlineResource(or)
# }
# distrib$setDigitalTransferOptions(dto)
# md$setDistributionInfo(distrib)
```

## Data Quality
Mandatory and expected items are not commented out while other items are commented out.

```{r pressure}
# dq <- ISODataQuality$new()
# scope <- ISOScope$new()
# scope$setLevel("dataset")
# dq$setScope(scope)
# 
# dc <- ISODomainConsistency$new()
# result <- ISOConformanceResult$new()
# spec <- ISOCitation$new()
# spec$setTitle("Data Quality check")
# spec$addAlternateTitle("This is is some data quality check report")
# d <- ISODate$new()
# d$setDate(as.Date(ISOdate(2015, 1, 1, 1)))
# d$setDateType("publication")
# spec$addDate(d)
# result$setSpecification(spec)
# result$setExplanation("some explanation about the conformance")
# result$setPass(TRUE)
# dc$addResult(result)
# dq$addReport(dc)
# 
# lineage <- ISOLineage$new()
# lineage$setStatement("statement")
# dq$setLineage(lineage)
# 
# md$setDataQualityInfo(dq)

```

## Create Metadata xml encoding and write xml files

```{r pressure, echo=FALSE}
# xml <- md$encode()
md$save("soy_iso_19115_metadata.xml")
```

